---
title: "MY WORK"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Getting a description of the data
The data was obtained from the kaggle website

the data was called car's dataset and it entailed the prices of second hand cars

The variables included in the data set include but not limited to

- Price
- Mileage
- type
- Make

## Getting the working directory and importing the data

```{r}
getwd()

Cars<-read.csv("Cars dataset.csv", stringsAsFactors = T, sep = ",")

View(Cars)

## Getting a summary of the data

summary(Cars)

```

## Creating Data Visualizations for the data

Creating a scatter plot for the price and Mileage variable

Loading the required libraries

```{r}
attach(Cars)

library(tidyverse)

scatter<-ggplot(data=Cars, mapping = aes(x= mileage,y=Price_Log10))+
  geom_point()+geom_smooth(method = "lm",se=T)+ 
  labs(x="Mileage of the Car", y= "Price of the car",
       title = "Scatter plot for Price and Mileage")+
  theme_classic()
scatter

```

## Creating a box plot for Price and type of transmission of a car

```{r}
boxplot<-ggplot(data=Cars,mapping = aes(x=Transmission,y=Price,fill=Transmission))+
  geom_boxplot()+labs(x=" Type of Transmission",y= "Price of a Car",
                      title = " Box plot for Price and type of transmission")+
  theme_classic()
boxplot

```


## SAving the formatted data to an RData file

```{r}
save(Cars,file = "Cars data.RData")

```

